Component-Based mruby Platform for IoT Devices

### 2018-02-12 ipsj/paper.tex
Fix the file format
Add the evaluation of TLSF+TECS

mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
Ruby is an object-oriented scripting language \cite{url:Ruby} with classes and methods, exceptions, and garbage collection functions.
It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.

@@

>>>>

mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard \cite{url:mruby}.
Ruby is an object-oriented scripting language \cite{url:Ruby} with classes and methods, exceptions, and garbage collection functions.
It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.

@@

\subsection{Memory usage of RiteVMs by TLSF+TECS}

The proposed dynamic memory allocator, TLSF+TECS, executes multiple tasks without exclusive control in parallel because each TLSF component holds its own heap area.
The TLSF+TECS framework provides functionality to acquire statistical information describing dynamic memory usage.
Therefore, it is possible to analyze the operational status of the TLSF and GC on RiteVMs.

Fig. \ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of two RiteVMs, with presented data acquired from the statistical information available via the TLSF+TECS framework.
From the figure, we observe that when the RiteVM are first activated, a large amount of memory is allocated for each RiteVM and initialization are performed within one second.
Next, the applications runs for ~10 s and the RiteVMs subsequently terminate.
The reduction in memory usage that occurs at regular intervals is due to the GC function of the RiteVM.
Here, an application that allocates tens of KB of memory runs on RiteVM 1 and an application that allocates hundreds of KB of memory runs on RiteVM 2.
Fig. \ref{fig:EvaluationOfMemoryUsageWithExclusiveContorol} shows the memory usage when two RiteVMs are executed in one heap area with exclusive control.
In Fig. \ref{fig:EvaluationOfDynamicConnection}, two applications are finished at 10.837 s, and in Fig. \ref{fig:EvaluationOfMemoryUsageWithExclusiveContorol}, they are finished at 10.877 s, which demonstrates that the execution time of the applications has increased by 0.3 \% due to exclusive contorol.

As such, the TLSF+TECS framework provides users with the ability to visualize GC behavior and help verify its operation.
Further, when the RiteVM terminates, the memory used by the RiteVM is not completely released, i.e., a few kilobytes remain.
This remaining memory causes a memory leak when the number of RiteVMs increases or a RiteVM repeatedly activates and shuts down.
Using the proposed environment here proves useful for detecting bugs related to memory, which in practice can be extremely difficult to detect.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/EvaluationOfTLSFStatistics.pdf}
    \caption{Memory usage of RiteVMs with TLSF+TECS}
    \label{fig:EvaluationOfTLSFStatistics}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/EvaluationOfMemoryUsageWithExclusiveContorol.pdf}
    \caption{Memory usage of RiteVMs with exclusive control}
    \label{fig:EvaluationOfMemoryUsageWithExclusiveContorol}
\end{figure}
